---
title: "Exercise 1"
author: Zhengyi Lin
output: md_document
---

```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(rsample)
library(caret)
library(modelr)
library(parallel)
library(foreach)
library(rsample)
```

## 1) Data visualization: flights at ABIA

```{r}
ABIA = read.csv("ABIA.csv")

AVG_Delay <- aggregate(DepDelay ~ AirTime, ABIA, mean)

ggplot(AVG_Delay, aes(x=AirTime, y=DepDelay))+
  geom_line()
```
If the air time is from 20-30 minutes, it is the least possible to delay. But if the air time is beween 250-300 minutes, it is the most likely to delay.


## 2) Wrangling the Olympics

### A

```{r}
olympics_top20=read.csv("olympics_top20.csv")
olympics_female<-olympics_top20 %>%
  filter(sex =="F", sport=='Athletics')

quantile(olympics_top20$height, probs=0.95)
```

### B
```{r}
olympics_female<-olympics_top20 %>%
  filter(sex =="F")

result<-split(olympics_female, olympics_female$event)%>%
  lapply(., function(x)sd(x$height))%>%
  unlist(.)%>%as.data.frame(.)
res<-cbind(row.names(result),result)
colnames(res)<-c("event","height_std_dev")

res_order<-res[order(res$height_std_dev, decreasing = TRUE),]

head(res_order)
```
### C
```{r}
olympics_swimmer <- olympics_top20 %>%
  filter(sport == 'Swimming')

AVG_Age_Swimmer <- aggregate(age ~ year, olympics_swimmer, mean)

AVG_Age_Gender <- aggregate(age ~ year + sex, olympics_swimmer, mean)

ggplot()+
  geom_line(data = AVG_Age_Swimmer, aes(x=year, y=age))+
  geom_smooth(span = 1)+
  geom_line(data=AVG_Age_Gender, aes(x=year, y=age, color = sex))
```
Before 1925, female's average age increase sharply. But after 1925, the average age decrease a lot until 1950. Female's average age is generally higher than male's average age.

## 3) K-nearest neighbors: cars
```{r}
sclass=read.csv("sclass.csv")
trim_350 <- sclass %>%
  filter(trim =='350') 
trim_65_AMG <- sclass %>%
  filter(trim == '65 AMG') 

trim_350_split =  initial_split(trim_350, prop=0.8)
trim350_train = training(trim_350_split)
trim350_test  = testing(trim_350_split)
trim_AMG_split = initial_split(trim_65_AMG, prop=0.8)
trimAMG_train = training(trim_AMG_split)
trimAMG_test = testing(trim_AMG_split)

# k-value cross validation
k_folds = 5

trim350_folds = crossv_kfold(trim_350, k=k_folds)
trimAMG_folds = crossv_kfold(trim_65_AMG,k=k_folds)

# define a series of k
k_grid = c(2, 4, 6, 8, 10, 15, 20, 25, 30, 35, 40, 45,
           50, 60, 70, 80, 90, 100, 125, 150, 175, 200)

cv_grid350 = foreach(k = k_grid, .combine='rbind') %dopar% {
  models = map(trim350_folds$train, ~ knnreg(price ~ mileage, k=k, data = ., use.all=FALSE))
  errs = map2_dbl(models, trim350_folds$test, modelr::rmse)
  c(k=k, err = mean(errs), std_err = sd(errs)/sqrt(k_folds)) 
} %>% as.data.frame

head(cv_grid350)

ggplot(cv_grid350) + 
  geom_point(aes(x=k, y=err)) + 
  geom_errorbar(aes(x=k, ymin = err-std_err, ymax = err+std_err)) + 
  scale_x_log10()

knn15 = knnreg(price ~ mileage, data=trim350_train, k=30)
modelr::rmse(knn15, trim350_test)

trim350_test = trim350_test %>%
  mutate(Price_pred = predict(knn15, trim350_test))

p_test = ggplot(data = trim350_test) + 
  geom_point(mapping = aes(x = mileage, y = price), alpha=0.2)

# add the predictions
p_test + geom_line(aes(x = mileage, y = Price_pred), color='red', size=1.5)



cv_gridAMG = foreach(k = k_grid, .combine='rbind') %dopar% {
  models = map(trimAMG_folds$train, ~ knnreg(price ~ mileage, k=k, data = ., use.all=FALSE))
  errs = map2_dbl(models, trimAMG_folds$test, modelr::rmse)
  c(k=k, err = mean(errs), std_err = sd(errs)/sqrt(k_folds))
} %>% as.data.frame

head(cv_gridAMG)

ggplot(cv_gridAMG) + 
  geom_point(aes(x=k, y=err)) + 
  geom_errorbar(aes(x=k, ymin = err-std_err, ymax = err+std_err)) + 
  scale_x_log10()

knn20 = knnreg(price ~ mileage, data=trim350_train, k=30)
modelr::rmse(knn20, trimAMG_test)

trimAMG_test = trimAMG_test %>%
  mutate(Price_pred = predict(knn20, trimAMG_test))

p_test = ggplot(data = trimAMG_test) + 
  geom_point(mapping = aes(x = mileage, y = price), alpha=0.2)

p_test + geom_line(aes(x = mileage, y = Price_pred), color='red', size=1.5)
```